Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2018-01-04 ms.tex
amps/offs

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/hst_model_comparison.pdf}
\caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM. The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag} = 10^3$ GCM. We also show the planet-to-star flux corresponding to each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.  \textbf{Right:} Temperature maps from the best fit models and the GCM at 0.1 bar.}
\label{fig:model_comparison}
\end{figure*}

@@

%\subsection{Clouds?}

\section{Atmospheric Composition and Thermal Structure}
\label{sec:composition}
To interpret the phase-resolved spectra, we performed two model fits. First, we modeled the planet flux as a simple blackbody to estimate the dayside brightness temperature and test for significant absorption or emission features. We then performed a more sophisticated grid-based retrieval to evaluate the atmospheric composition and thermal structure.

>>>>

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/hst_model_comparison.pdf}
\caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM. The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag} = 10^3$ GCM. We also show the planet-to-star flux corresponding to each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.  \textbf{Right:} Temperature maps from the best fit models and the GCM at 0.1 bar. FIXME say here what the temperature difference is at substellar point.}
\label{fig:model_comparison}
\end{figure*}

@@

FIXME what is the weighted mean amplitude and offset for the WFC3 data? are they all consistent?

\begin{deluxetable}{LLL}
	\tablecolumns{3}
	\tablewidth{0pt}:
	\tablecaption{Phase Curve Properties \label{table:amps_offsets}}
	\tablehead{
	\colhead{Wavelength} & \colhead{Amplitude} & \colhead{Offset}}
		\startdata
		1.175 & 0.89 \pm 0.17 & -0.3 \pm 1.3 \\
		1.225 & 1.11 \pm 0.27 & -1.8 \pm 1.3 \\
		1.275 & 0.88 \pm 0.17 & 1.1 \pm 1.4 \\
		1.325 & 0.92 \pm 0.17 & 0.6 \pm 1.4 \\
		1.375 & 0.82 \pm 0.14 & 1.8 \pm 1.5 \\
		1.425 & 0.91 \pm 0.16 & 1.6 \pm 1.4 \\
		1.475 & 0.83 \pm 0.13 & 2.5 \pm 1.4 \\
		1.525 & 1.04 \pm 0.19 & 0.3 \pm 1.2 \\
		1.575 & 0.99 \pm 0.19 & -0.3 \pm 1.3 \\
		1.625 & 0.86 \pm 0.18 & -1.8 \pm 1.2 \\
		\enddata
	\end{deluxetable}

%\subsection{Clouds?}
\section{Atmospheric Composition and Thermal Structure}
\label{sec:composition}
To interpret the phase-resolved spectra, we performed two model fits. First, we modeled the planet flux as a simple blackbody to estimate the dayside brightness temperature and test for significant absorption or emission features. We then performed a more sophisticated grid-based retrieval to evaluate the atmospheric composition and thermal structure.
